### 2015-03-16 Docs/managing_jobs/managingjobs.tex
update rhea vis

>>>>

\subsubsection{Rhea---preferred method}

The best way to do visualization is to use rhea, the OLCF vis machine.
You need to build \yt\ via the {\tt install\_script.sh} script {\em on
rhea}.  It also must be on a Lustre filesystem, so it is seen by
the compute node.  It is best to build it in your {\tt \$PROJWORK} directory,
since that has a longer time between purges.  Once the installation is
complete, it will tell you what script to source to define the
necessary paths.

The scripts in {\tt MAESTRO/Util/job\_scripts/rhea/} will handle the
visualization.  On rhea, the job script gives you access to the
compute node, and then you can run serial jobs or a parallel job with
{\tt mpirun}.  The {\tt process-rhea.run} script will request the
resources and run the {\tt parallel-yt-rhea} script.  {\tt
parallel-yt-rhea} will launch the visualization process (defined
via the variables at the top of the script) on all the plotfiles
found to match the prefix defined in the script.  Several serial
jobs are run together, with the script using lock files to keep track
of how many processors are in use.  When processors free, the next
file in the list is processed, and so on, until there are no more
plotfiles left to process.  If a {\tt .png} file matching the
plotfile prefix is found, then that plotfile is skipped.

\subsubsection{Titan}
